The Heavy Photon Search Test Detector

### 2013-11-13 hps-testrun-nim.tex
Tim's shortening of SVT detector section.

The principle purpose of the HPS Test Silicon Vertex Tracker (SVT) is the efficient detection of 
charged particles and reconstruction of their momentum and angles. The precise measurements 
forms the primary input to the extraction of a signal from \Aprime{} decays; both from the precise 
measurement of the invariant mass of its \ee{} decay products and the position of its decay vertex 
downstream of the target. Track reconstruction is also important for energy scale calibration of the 
electromagnetic calorimeter due to the better momentum resolution of tracks compared to clusters 
in the calorimeter.

\subsection{SVT Requirements and Constraints}
%The primary goal was to demonstrate that the technology and design approach 
%chosen for the SVT was sound for running in the challenging environment at JLab. 
%Nevertheless, a secondary but 
%important aspect was that, after proving the technical concepts,  the apparatus would have the 
%capability to discover \Aprime{} events. The implication was that the design of the SVT in the 
%HPS Test apparatus would be subject to almost the same constraints and requirements as the full 
%experiment except for certain aspects regarding longevity and robustness subject to cost, beam time 
%and construction and design time constraints for the Test run.

@@

It is this last challenge that has the most interesting and obvious impacts on the design of the SVT. To 
achieve good vertexing performance, the first layer must be placed no more than about 10 cm downstream 
of the target. At that distance, it is found that the active region of a sensor can be placed as close to 1.5 mm 
from the center of the beam, defining a 15 mrad ``dead zone" in the detector around the plane of the 
primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, as shown in 
Fig.~\ref{fig:radiation} and~\ref{fig:rates}.
%===================
\begin{figure}[]
\includegraphics[width=7cm]{figures/radiation}
\label{fig:radiation}
\caption{\small Simulation of the fluence 10~cm downstream of the target in the active region of the SVT ($|Y|>0.15~$cm) looking downstream; electrons bend towards $+x$.}
\end{figure}
%===================
%===================
\begin{figure}[]
\includegraphics[width=7cm]{figures/rates}
\label{fig:rates}
\caption{\small Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
vertical distance from the beam center.}
\end{figure}
%=================== 
This requires the sensors to be actively cooled. Meanwhile, very low-energy delta rays from beam gas interactions multiply the density of background hits, so the SVT must operate inside the beam vacuum.  Finally, in order to protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.  
%To summarize the SVT must:
%\begin{itemize}
%\item have a uniform acceptance in the forward region; up to $\theta_y=XXXXmrad$ and as close as 
%possible to the beam axis to catch boosted decay products,
%\item >95\% reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
%\item momentum resolution of XXXX\% to separate a promptly decaying \Aprime{} signal from the irreducible background,
%\item vertex resolution $<XXXX$~mm along the beam line direction to search for displaced \Aprime{} decays,
%\item event timing resolution down to 2~ns, 
%\item sustain a occupancy of up to 1\%, trigger rates of $\approx50$~kHz and data rates up to 100~MB/s,
%\item survive and efficiently operate after $1\times10^{14} neutron eq. fluence,
%
%dosedetector components that can survive and efficiently operate in a high radiation environment with 
%local doses exceeding $XXXX$~MRad
%\end{itemize}

\subsection{SVT Layout}

A realistic \geant{}~\cite{Agostinelli2003250} simulation of the detector based on the {\sc SLIC} simulation 
package~\cite{Graf:2011zzc}
including all backgrounds has been used to optimize the layout for acceptance, tracking efficiency, mass 
resolution and prompt vertex rejection. The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}.

The vertex resolution with an asymmetric beam spot of $\approx200\times40~\mu$m requires hit 
resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
In addition, the vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize 
the vertex resolution in the horizontal coordinate. Instead, 100~mrad stereo is used in the first three layers 
to provide higher-resolution 3D space points for vertexing. The 50~mrad stereo of the last two layers 
breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits, 
improving pattern recognition while still providing sufficient pointing resolution into the third layer
 for robust hit 
association in the denser environment there. Altogether, this layout comprises 20 sensors and hybrids and 
100 APV25 chips for a total of 12780 readout channels. 
%=======================
\begin{center}
\begin{table}[ht]
{\small
\begin{tabular}{lccccc}   
\hline \hline 
    Layer & 1 & 2 & 3 & 4 & 5 \\      
\hline
    $z$ from nom. target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
    Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
    Bend res. ($\mu$m)  & $\approx$60 & $\approx$60 & $\approx$60 & $\approx$120 & $\approx$120  \\ 
    Non-bend res. ($\mu$m)  & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6  \\ 
    \# of sensors  & 4 & 4 & 4 & 4 & 4  \\ 
    Dead zone (mm) & $\pm1.5$  & $\pm3.0$  & $\pm4.5$  & $\pm7.5$  & $\pm10.5$  \\ 
    Power cons. (W) & 6.9 & 6.9 & 6.9 & 6.9 & 6.9 \\
\hline \hline
\end{tabular}
\caption{\small Layout of the HPS Test SVT.. }
}
\label{tab:trk} 
\end{table}
\end{center}
%=======================
\begin{center}
\begin{figure}[htp]
    \includegraphics[width=7cm]{figures/HPS_nochamber}
\caption{\small A rendering of the HPS Test SVT showing the modules on their support plates held by the 
hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the hybrid 
readout boards in green. The beam enters from the right through a vacuum box with flanges for services. }
\label{fig:tracker_model}
\vspace*{-5mm}
\end{figure}
\end{center}
%=======================
The SVT is built in two separate halves that are mirror reflections of one another about the plane of the 
nominal electron beam.  Each half consists of five, double-sided modules mounted on a support plate that 
provides services to the modules and allows them to be moved as a group relative to the dead zone. The 
two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond the last layer t
that defines the nominal spacing between the upper and lower halves of the tracker.  A shaft attached to each 
support plate in front of layer 1 extends upstream and connects to a linear shift that transfers motion into the 
vacuum box through bellows to open and close the two halves around the dead zone. The C-support is 
mounted to an aluminum baseplate that defines the position of the SVT with respect to the vacuum 
chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both completed detector halves prior to 
final assembly. 
%=======================
\begin{figure}[htp]
\begin{center}
    \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
\caption{\small{Both halves of the HPS Test SVT after final assembly at SLAC.  The cooling manifolds and 
integrated cable runs are clearly seen.} }
\label{fig:tracker_halves}
\end{center}
\vspace*{-5mm}
\end{figure}
%=======================

\subsection{SVT Components}

\subsubsection{Silicon Sensors}
The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run.  This 
corresponds to about 4~MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
very high local occupancies. Since sensitivity is limited by multiple scattering, a material budget of less 
than 1\% $X_0$/layer is imperative and far less is desirable. To achieve the required vertex resolution  
single-hit resolutions better than XXXX~$\mu$m are required. Finally, the sensor technology must 
be mature and readily available at low cost.  Silicon microstrips are the best match to these requirements, and 
a supply of appropriate microstrip sensors purchased from the Hamamatsu Photonics Corporation for the 
Run 2b upgrade of the D\O experiment~\cite{Denisov:2001aa} are readily available. 
These are $p+$-on-$n$, single sided, AC coupled, 
polysilicon-biased sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch 
over their $4\times10$~cm$^2$ surface. Although a maximum bias of 350~V is specified, the vast majority are 
operable to 1000~V and therefore remain fully depleted to a dose of approximately 
$1.5\times10^{14}$~\fluenceunit{}.

\subsubsection{Front-end Electronics}
Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
strip see a significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
trigger window and tagging of hit times to roughly 8~ns, as shown in Fig.~\ref{fig:rates}.  The FADC 
readout for the ECal and muon system are capable of this (see Sec.~\ref{sec:fadc}), but achieving 
$2\sigma$ efficiency for 
silicon hits then requires 2~ns time resolution for the hits in the SVT. This performance can be achieved with 
the APV25 readout ASIC developed for the CMS experiment at CERN~\cite{French:2001xb}.  When 
operated in ``multi-peak mode", the APV25 captures successive samples of the output of the shaper in sets 
of three at a sampling rate of approximately 40~MHz.  
By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
determined to a precision of 2~ns for S/N$>25$, an achievable figure with our sensors if read out 
individually~\cite{Friedl:2009zz}.  For the SVT, six-sample readout and the shortest possible shaping time 
(35~ns) will be used to best distinguish hits that overlap in time.
The APV25 ASICs are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
outside the tracking volume.  Along with the sensors, these are assembled into half-modules, one for each 
tracking view, with a short cable pigtail to provide power and configuration to the modules and signal 
readout.

\subsubsection{Support Structure and Cooling}

@@

\subsection{SVT Digitization, Event Building and Data Transmission}
\label{sec:svt_daq}
The SVT data acquisition (DAQ) based on the Reconfigurable Cluster Element (RCE) and Cluster 
Interconnect (CI) concept developed at SLAC as generic building blocks for DAQ systems in high energy 
physics . The RCE is a generic computational building block, housed on a separate daughter card 
called Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On 
Board (COB), see Fig.~\ref{fig:cob}.
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/svt_daq_module}
	\caption{Picture of the SVT DAQ COB board with four data processing daughter cards visible.}
	\label{fig:cob}
}
\end{center}
\end{figure}
The Gen-I RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
The outputs of 12 SVT half-modules 
are digitized on the Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, 
interfacing the HPS readout to the generic DAQ components on the COB. 
A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to the sensitive 
range of a 14-bit ADC operating at the system clock of 41.667~MHz. 
The RTM is organized into four sections with each section supporting three SVT half-module hybrids (15 
APV25 channels). The RTM also includes a 4-channel Fiber Optic module and supporting logic which can be 
used to interface to the JLab trigger system supervisor.
Each section of the RTM, up to three hybrids, is input to a DPM which apply thresholds for data reduction and 
organizes the sample data into UDP datagrams. The DPM also hosts an I2C controller used to configure and 
monitor the APV25 chips on those three hybrids. A single ATCA crate with two COB cards was used, one 
supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as the trigger and data 
transmission module. The two COB cards and their DPMs are interconnected with a 10Gb/s switch 
card~\cite{Larsen:2011zb} which 
also hosts two 1Gb/s Ethernet interfaces to the external SVT DAQ PC.

@@

Hybrid readout boards and half-modules were assembled at SLAC.  Mounting APV25 chips and all 
wirebonding and QA testing were performed at University of California, Santa Cruz. Of the sensors tested 
during production, 90\% were capable of 1000~V bias voltage without breakdown. 
Hybrids underwent quick QA testing and each half-module was run at low 
temperature ($\approx5^{\circ}$ C) and fully characterized for pedestals, gains, noise and time response 
after assembly.  All 29 production modules were assembled between mid-February and the end of March, 
2012.  Module yields were excellent for such a small production.  Of 165 APV chips acquired, 150 were 
used to assemble 30 production hybrids, of which 29 passed QA testing.  Of 29 half-modules built, 28 passed 
QA testing, leaving 8 spare modules after completion of the SVT.  Full-module assembly and 
mechanical surveys were performed at SLAC in early April 2012 before final assembly, testing and 
shipping of the SVT to JLab on April 11.  A custom shipping container, based on experience 
from FNAL~\cite{shipping}, was built in order to safely send the partly assembled SVT to JLab. The two fully 
assembled SVT halves were attached to a baseplate supported by four wire-rope isolators. This plate, 
covered by a lexan cover for cleanliness, was mounted inside an inner box surrounded by 4 inches of 
Polyurethane foam to complete the two-spring construction. At JLab, the entire SVT was integrated with the full 
DAQ and the power supplies for the first time in the clean room, before moving the module-loaded support 
plates to Hall~B for final mechanical assembly and installation inside of the vacuum chamber on April 19, 2012.

\subsection{Alignment}
The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
optical survey of individual modules with precision of a few $\mu$m are combined with a touch-prove survey 
of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the silicon sensor layers with 
respect to the support plates and the mechanical survey balls on the base plate.
After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate position 
inside the pair spectrometer vacuum chamber is used to determine the global position of the SVT with 
respect to CEBAF beam line. 
The resulting survey-based alignment has the position of the silicon sensors correct to within a few hundred 
microns. A more sophisticated global track-based alignment technique to reach the final alignment precision 
is being developed.

@@

\section{Electromagnetic Calorimeter}
\label{sec:ecal}
\section{Electromagnetic Calorimeter}
\label{ecal}

@@

\subsection{ECal Components}

>>>>

The Silicon Vertex Tracker (SVT) enables efficient reconstruction of charged particles and precision 
determination of their trajectories. These measurements allow \Aprime{} decays to be distinguished from background 
via simultaneous estimation of the invariant mass of \ee{} decay products and the position of decay vertexes 
downstream of the target.

%Track reconstruction is also important for energy scale calibration of the electromagnetic calorimeter due to the better momentum resolution of tracks compared to clusters in the calorimeter.

%\subsection{SVT Requirements and Constraints}
%The primary goal was to demonstrate that the technology and design approach 
%chosen for the SVT was sound for running in the challenging environment at JLab. 
%Nevertheless, a secondary but 
%important aspect was that, after proving the technical concepts,  the apparatus would have the 
%capability to discover \Aprime{} events. The implication was that the design of the SVT in the 
%HPS Test apparatus would be subject to almost the same constraints and requirements as the full 
%experiment except for certain aspects regarding longevity and robustness subject to cost, beam time 
%and construction and design time constraints for the Test run.

@@

It is this last challenge that has the most interesting and obvious impacts on the design of the SVT. To 
achieve good vertexing performance, the first layer must be placed no more than about 10 cm downstream 
of the target. At that distance, it is found that the active region of a sensor can be placed as close to 1.5 mm 
from the center of the beam, defining a 15 mrad ``dead zone" in the detector around the plane of the 
primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, as shown in 
Fig.~\ref{fig:radiation}.
% and~\ref{fig:rates}.
%===================
\begin{figure}[]
\includegraphics[width=7cm]{figures/radiation}
\label{fig:radiation}
\caption{\small Simulation of the fluence 10~cm downstream of the target in the active region of the SVT ($|Y|>0.15~$cm) looking downstream; electrons bend towards $+x$.}
\end{figure}
%===================
%===================
%\begin{figure}[]
%\includegraphics[width=7cm]{figures/rates}
%\label{fig:rates}
%\caption{\small Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
%vertical distance from the beam center.}
%\end{figure}
%=================== 
This requires the sensors to be actively cooled. Meanwhile, very low-energy delta rays from beam gas interactions multiply the density of background hits, so the SVT must operate inside the beam vacuum.  Finally, in order to protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.  
%To summarize the SVT must:
%\begin{itemize}
%\item have a uniform acceptance in the forward region; up to $\theta_y=XXXXmrad$ and as close as 
%possible to the beam axis to catch boosted decay products,
%\item >95\% reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
%\item momentum resolution of XXXX\% to separate a promptly decaying \Aprime{} signal from the irreducible background,
%\item vertex resolution $<XXXX$~mm along the beam line direction to search for displaced \Aprime{} decays,
%\item event timing resolution down to 2~ns, 
%\item sustain a occupancy of up to 1\%, trigger rates of $\approx50$~kHz and data rates up to 100~MB/s,
%\item survive and efficiently operate after $1\times10^{14} neutron eq. fluence,
%
%dosedetector components that can survive and efficiently operate in a high radiation environment with 
%local doses exceeding $XXXX$~MRad
%\end{itemize}

A realistic \geant{}~\cite{Agostinelli2003250} simulation of the detector based on the {\sc SLIC} simulation 
package~\cite{Graf:2011zzc}, including all backgrounds, has been used to optimize the layout for acceptance, tracking efficiency, mass 
resolution and prompt vertex rejection. The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}. 
%Vertex resolution with an asymmetric beam spot of $\approx200\times40~\mu$m requires hit resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
%In addition, the vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize the vertex resolution in the horizontal coordinate. Instead, 
100~mrad stereo is used in the first three layers to provide higher-resolution 3D space points for vertexing. 50~mrad stereo in the last two layers breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits, 
improving pattern recognition while still providing sufficient pointing resolution into the third layer for robust hit association in the denser environment there. Altogether, this layout comprises 20 sensors and hybrids and 100 APV25 chips for a total of 12780 readout channels. 
%=======================
\begin{center}
\begin{table}[ht]
{\footnotesize
\begin{tabular}{lccccc}   
\hline \hline 
    Layer & 1 & 2 & 3 & 4 & 5 \\      
\hline
    $z$ from target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
    Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
    Bend res. ($\mu$m)  & $\approx$60 & $\approx$60 & $\approx$60 & $\approx$120 & $\approx$120  \\ 
    Non-bend res. ($\mu$m)  & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6  \\ 
    \# of sensors  & 4 & 4 & 4 & 4 & 4  \\ 
    Dead zone (mm) & $\pm1.5$  & $\pm3.0$  & $\pm4.5$  & $\pm7.5$  & $\pm10.5$  \\ 
    Power cons. (W) & 6.9 & 6.9 & 6.9 & 6.9 & 6.9 \\
\hline \hline
\end{tabular}
\caption{\small Layout of the HPS Test SVT.}
}
\label{tab:trk}
\vspace*{-15mm}
\end{table}
\end{center}
%=======================
\begin{center}
\begin{figure}[htp]
    \includegraphics[width=7cm]{figures/HPS_nochamber}
\caption{\small A rendering of the HPS Test SVT showing the modules on their support plates held by the 
hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the hybrid 
readout boards in green. The beam enters from the right through a vacuum box with flanges for services. }
\label{fig:tracker_model}
%\vspace*{-5mm}
\end{figure}
\end{center}
%=======================
The SVT is built in two separate halves that are mirror reflections of one another about the plane of the 
nominal electron beam.  Each half consists of five, double-sided modules mounted on a support plate that 
provides services to the modules and allows them to be moved as a group relative to the dead zone. The 
two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond the last layer t
that defines the nominal spacing between the upper and lower halves of the tracker.  A shaft attached to each 
support plate in front of layer 1 extends upstream and connects to a linear shift that transfers motion into the 
vacuum box through bellows to open and close the two halves around the dead zone. The C-support is 
mounted to an aluminum baseplate that defines the position of the SVT with respect to the vacuum 
chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both completed detector halves prior to 
final assembly. 
%=======================
\begin{figure}[htp]
\begin{center}
    \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
\caption{\small{Both halves of the HPS Test SVT after final assembly at SLAC.  The cooling manifolds and 
integrated cable runs are clearly seen.} }
\label{fig:tracker_halves}
\end{center}
\vspace*{-5mm}
\end{figure}
%=======================

\subsection{Components}

%\subsubsection{Silicon Sensors}
The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run.  This 
corresponds to about 4~MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
very high local occupancies. Since sensitivity is limited by multiple scattering, a material budget of less 
than 1\% $X_0$/layer is imperative and far less is desirable. To achieve the required vertex resolution  
single-hit resolutions better than XXXX~$\mu$m are required. Finally, the sensor technology must 
be mature and readily available at low cost.  Silicon microstrips are the best match to these requirements, and 
a supply of appropriate microstrip sensors purchased from the Hamamatsu Photonics Corporation for the 
Run 2b upgrade of the D\O experiment~\cite{Denisov:2001aa} are readily available. 
These are $p+$-on-$n$, single sided, AC coupled, 
polysilicon-biased sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch 
over their $4\times10$~cm$^2$ surface. Although a maximum bias of 350~V is specified, the vast majority are 
operable to 1000~V and therefore remain fully depleted to a dose of approximately 
$1.5\times10^{14}$~\fluenceunit{}.

%\subsubsection{Front-end Electronics}
Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
strip see a significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
trigger window and tagging of hit times to roughly 8~ns.  The FADC 
readout for the ECal and muon system are capable of this (see Sec.~\ref{sec:fadc}), but achieving 
$2\sigma$ efficiency for 
silicon hits then requires 2~ns time resolution for the hits in the SVT. This performance can be achieved with 
the APV25 readout ASIC developed for the CMS experiment at CERN~\cite{French:2001xb}.  When 
operated in ``multi-peak mode", the APV25 captures successive samples of the output of the shaper in sets 
of three at a sampling rate of approximately 40~MHz.  
By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
determined to a precision of 2~ns for S/N$>25$, an achievable figure with our sensors if read out 
individually~\cite{Friedl:2009zz}.  For the SVT, six-sample readout and the shortest possible shaping time 
(35~ns) will be used to best distinguish hits that overlap in time.
The APV25 ASICs are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
outside the tracking volume.  Along with the sensors, these are assembled into half-modules, one for each 
tracking view, with a short cable pigtail to provide power and configuration to the modules and signal 
readout.

%\subsubsection{Support Structure and Cooling}

@@

\subsection{Digitization, Event Building and Data Transmission}
\label{sec:svt_daq}
The SVT data acquisition (DAQ) based on the Reconfigurable Cluster Element (RCE) and Cluster 
Interconnect (CI) concept developed at SLAC as generic building blocks for DAQ systems in high energy 
physics {\bf [need reference]}. 
The RCE is a generic computational building block, housed on a separate daughter card called 
Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board (COB), 
see Fig.~\ref{fig:cob}.
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/svt_daq_module}
	\caption{Picture of the SVT DAQ COB board with four data processing daughter cards visible.}
	\label{fig:cob}
}
\end{center}
\end{figure}
The Gen-I RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
The outputs of 12 SVT half-modules are digitized on the Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the COB. 
A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to the sensitive 
range of a 14-bit ADC operating at the system clock of 41.667~MHz. 
The RTM is organized into four sections with each section supporting three SVT half-module hybrids (15 
APV25 channels). The RTM also includes a 4-channel Fiber Optic module and supporting logic which can be 
used to interface to the JLab trigger system supervisor.
Each section of the RTM, up to three hybrids, is input to a DPM which apply thresholds for data reduction and 
organizes the sample data into UDP datagrams. The DPM also hosts an I2C controller used to configure and 
monitor the APV25 chips on those three hybrids. A single ATCA crate with two COB cards was used, one 
supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as the trigger and data 
transmission module. The two COB cards and their DPMs are interconnected with a 10Gb/s switch 
card~\cite{Larsen:2011zb} which 
also hosts two 1Gb/s Ethernet interfaces to the external SVT DAQ PC.

@@

%Hybrid readout boards and half-modules were assembled at SLAC.  Mounting APV25 chips and all wirebonding and QA testing were performed at University of California, Santa Cruz.

Of the sensors tested during production, 90\% were capable of 1000~V bias voltage without breakdown. 
Hybrids underwent quick QA testing and each half-module was run at low temperature ($\approx5^{\circ}$ C) and 
fully characterized for pedestals, gains, noise and time response after assembly.  
%All 29 production modules were assembled between mid-February and the end of March, 2012.  Module yields were excellent for such a small production.  Of 165 APV chips acquired, 150 were used to assemble 30 production hybrids, of which 29 passed QA testing.  
Of 29 half-modules built, 28 passed 
QA testing, leaving 8 spare modules after completion of the SVT.  Full-module assembly and 
mechanical surveys were performed at SLAC
% in early April 2012 
before final assembly, testing and shipping of the SVT to JLab
% on April 11.  
A custom shipping container with nested crates and redundant isolation for shock and vibration 
%, based on experience from FNAL~\cite{shipping},
was built in order to safely send the partly assembled SVT to JLab. 
% The two fully assembled SVT halves were attached to a baseplate supported by four wire-rope isolators. This plate, covered by a lexan cover for cleanliness, was mounted inside an inner box surrounded by 4 inches of Polyurethane foam to complete the two-spring construction. 
At JLab, the entire SVT was integrated with the full DAQ and the power supplies 
%for the first time in the clean room, 
before moving the module-loaded support plates to Hall~B for final mechanical assembly and installation inside of the 
vacuum chamber.
% on April 19, 2012.

\subsection{Alignment}
The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
optical survey of individual modules with precision of a few $\mu$m are combined with a touch-probe survey 
of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the silicon sensor layers with 
respect to the support plates and the mechanical survey balls on the base plate.
After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate position 
inside the pair spectrometer vacuum chamber is used to determine the global position of the SVT with 
respect to CEBAF beam line. 
The resulting survey-based alignment has the position of the silicon sensors correct to within a few hundred 
microns. A more sophisticated global track-based alignment technique to reach the final alignment precision 
is being developed.

@@

\section{Electromagnetic Calorimeter}
\label{sec:ecal}

@@

\subsection{Components}
